### 2015-06-26 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update to report and figures

The fire suppression series included 14 tests in two single-story experimental structures. Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent.

Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings. The nozzle patterns were varied from straight stream to narrow fog, and in the case of the two attic tests, a smooth bore nozzle was used. Several other factors including the fuel load and available ventilation were varied during these tests.

Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.  The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.  The fires were intended to replicate room and contents fires typically seen within residential structures.  The hose lines were pre-deployed with fixed nozzles set in two locations.  One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle). The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack. The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.  This position represented a direct interior attack.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
	\caption{Hallway Nozzle Location for Fire Suppression Tests}
	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
	\caption{Room Nozzle Location for Fire Suppression Tests}
	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
\end{figure}

Due to the limited time and resources for testing, the extremes were chosen: smooth bore and narrow fog.

Straight stream from a fog nozzle was the medium between the two.

@@

\subsection{Purpose Built Fire Training Structure - Gas Cooling}
\label{sec:Burn_Building}

The burn building is a purpose-built live fire training structure comprised of both a two story and three story section. The building is supported with reinforced concrete beams and columns.  The floors and ceilings are also concrete with the interior walls constructed of cement block. The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thick layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile. The floor of the burn rooms is protected with fire brick.

@@

The two room configuration within the burn building had overall dimensions of 6.5 m (21.3 ft) by 9.2 m (30.2 ft). The burn room where the fuel load was located measured 3.8 m (12.5 ft) by 5.7 m (18.7 ft) with a ceiling height of 3.35 m (11.0 ft). The adjacent room where the water was applied for gas cooling measured 4.1 m (13.4 ft) by 5.7 m (18.7 ft), also with a ceiling height of 3.35 m (11.0 ft). The open door from the adjacent room to the exterior measured 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.

@@

Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.  The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

@@

Each structure had burn room, approximately 6.0 m (19.6 ft) by 4.4 m (14.3 ft) and 2.74 m (9.0 ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.  The hallway is approximately 0.95 m (3.1 ft) wide and 5.4 m (17.6 ft) and the entry foyer is 1.2 m (4.1 ft) by 1.9 m (6.1 ft).  The ceiling height in the hallway and entry foyer was 2.4 m (8 ft).  The open door on north side from the exterior to the entry foyer was 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.  The opening on the south face of the structure from the exterior to the burn room was 2.4 m (7.75 ft) high and 1.09 m (3.6 ft) wide.   A schematic plan view of the structure is given in Figure     .

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
	\caption{Delaware County, PA Fire Test Structure}
	\label{fig:DelCoSingleStory}
\end{figure}

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression}

>>>>

The fire suppression series included 14 tests in two single-story experimental structures. Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent. The nozzle patterns were varied from straight stream to narrow fog. Two additional tests were conduction on suppression tactics for attic fires in residential dwellings, one in each structure. For these tests, a smooth bore nozzle was used.

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
% 	\caption{Hallway Nozzle Location for Fire Suppression Tests}
% 	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
% 	\caption{Room Nozzle Location for Fire Suppression Tests}
% 	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
% \end{figure}

@@

\subsection{Fire Training Structure - Gas Cooling}
\label{sec:Burn_Building}

The burn building is a live fire training structure with both a two story and three story section. The building is supported with reinforced concrete beams and columns. The floors and ceilings are also concrete with the interior walls constructed of cement block. The walls and ceiling of the burn rooms are protected with a 25~mm thick layer of calcium silicate insulation and is covered by a 50~mm thick concrete tile. The floor of the burn rooms is protected with fire brick. Tests were conducted in the two-story, two-room configuration which has overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (cf. Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).

@@

The burn room where the fuel load was located measured 3.8~m (12.5~ft) by 5.7~m (18.7~ft) with a ceiling height of 3.35~m (11.0~ft). The adjacent room where the water was applied for gas cooling measured 4.1~m (13.4~ft) by 5.7~m (18.7~ft), also with a ceiling height of 3.35~m (11.0~ft). The open door from the adjacent room to the exterior measured 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.

@@

Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61~m (2~ft) wide, 0.61~m (2~ft) high and 1.22~m (4~ft) long.  The interior dimensions of each structure were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

@@

Each structure had burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer. The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft). The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).  The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.  The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide. A dimensioned, plan view of the structure is included in Fig.~\ref{fig:Test_Structure_Floor_Plan}.

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
% 	\caption{Delaware County, PA Fire Test Structure}
% 	\label{fig:DelCoSingleStory}
% \end{figure}

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression}	
Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.  The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.  The fires were intended to replicate room and contents fires typically seen within residential structures.  The hose lines were pre-deployed with fixed nozzles set in two locations.  One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle). The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack. The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.  This position represented a direct interior attack.
